\section*{Methods}
\subsection*{Participants}
some people were tested...
\subsection*{Stimuli}
Eight stimuli were used during this experiment: four rhythmic patterns and four rhythm-matched speech patterns (See Figure  ). 
Each stimulus was preceded by four metronome clicks to cue the participant to the tempo (120 bpm). 
After 12 seconds, the stimulus stopped playing, the metronome continued, and participants were asked to imagine the stimulus just as they had heard it for another 12 seconds. 
Rhythmic patterns were played in a random order during the first half of the experiment and speech patterns were played in a random order during the second half. 
Each stimulus was heard and imagined 12 times throughout the experiment. 
\subsection*{Equipment and Procedure}
We collected information about participants' previous musical experience, their ability to imagine sounds, and musical sophistication using an adapted version of the Goldsmith's Musical Sophistication Index () combined with a clarity of auditory imagination scale(). 
During the experiment, participants were seated in an audiometric room (Eckel model CL-13) and the EEG data were collected using a BioSemi Active-Two system with 64+2 EEG channels. 
Horizontal and vertical EOG channels were used to record eye movements. EEG was sampled at 512 Hz. 
A Cedrus StimTracker was used to ensure minimal delay ($<$0.05 ms) between the presentation of the stimulus to the participant and the marking of stimulus onset in the data. 
The experiment was programmed and presented using PsychToolbox run in MATLAB 2014a. A computer monitor displayed the instructions and speakers played the stimuli at a comfortable volume for each participant. 
While listening and imagining, participants were presented with a fixation cross and asked to keep their gaze steady.
The volume of the stimuli was kept constant across participants.
\subsection*{EEG Data Processing}
EEG pre-processing was done using EEGLab. 
Data were filtered between 0.5Hz and 30Hz, downsampled to 256Hz, epoched to remove break-periods, and submitted to an ICA analysis.
ICA components corresponding to artefacts (eyeblinks, heart rate, etc.) were manually removed.
Clean EEG data were exported from EEGLab into Fieldtrip for frequency analyses.
Using the fieldtrip ft\_freqanalysis function, a fourier wavelet analysis was performed. 